---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# JobSearchAssistance

The user benefit from an artificial intelligence to assist him in his job search or paid assignments.

The tool allows you to collect, analyze and classify job offers according to your own tastes. 
Matching an offer allows the algorithm to know your preferences.

The project is divided into three phases:

  + Data collection using web scrapping with the get() function.
  + The app() function allows you to swap and classify the offers. 
  + Finally, the algo() function analyze the remaining offers and predict a sensitivity score.

# Application 

## Identify research using keywords

```{r eval = FALSE}
## Réssources
lapply(list.files("inst/", full.names = T), source)
```

```{r eval = FALSE}
## Inputs
params = list(
  user_id   = "tintin",
  mots_cles = c("data+scientist", "Statisticien")
  )
```

## Scrape a list of offers

```{r eval = FALSE}
get(mc = params$mots_cles, id = params$user_id)
```

## Manually classify (swap) the offers

```{r eval = FALSE}
app(id = params$user_id)
```

## Learn from the result and predict the classification of unclassified

```{r eval = FALSE}
algo(id = params$user_id)
```

## Offer the most likely to please offers

```{r include=FALSE}
require(tidyverse)
```

```{r}
read_rds("data/top/prev.RDS") %>% 
  slice_head(n = 10)
```


