---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# JobSearchAssistance

The user benefit from an artificial intelligence to assist him in his job search or paid assignments.

The tool allows you to collect, analyze and classify job offers according to your own tastes. 
Matching an offer allows the algorithm to know your preferences.

The project is divided into three phases:

  + Data collection using web scrapping with the get() custom function.
  + The app() function allows you to swap and classify the offers. 
  + Finally, the algo() function analyze the remaining offers and predict a sensitivity score.

# Identifier la recherche grâce à des mots clés (Intitulé du poste + type de contrat + zone)

```{r eval = FALSE}
# Réssources
lapply(list.files("inst/", full.names = T), source)
```

```{r eval = FALSE}
# Inputs
params = list(
  user_id   = "tintin",
  mots_cles = c("data+scientist", "Statisticien")
  )
```

# Scraper une liste d'offres

```{r eval = FALSE}
get(mc = params$mots_cles, id = params$user_id)
```

# Classer manuelement (swap) les offres

```{r eval = FALSE}
app(id = params$user_id)
```

# Apprendre du résultat et prédir la classification des non classés

```{r eval = FALSE}
algo(id = params$user_id)
```

# Proposer les offres les plus succeptible de plaire

```{r include=FALSE}
require(tidyverse)
```

```{r}
read_rds("data/top/prev.RDS") %>% 
  slice_head(n = 10)
```


